Higher-Order unification for free!

### 2024-07-01 paper/main.tex
"for the Coq’s system" => "for Coq's type system"

\section{Introduction}
\label{sec:intro}
We aim to implement a
form of proof search known as type-class resolution~\cite{wadler89,sozeau08}
for the Coq's system~\cite{Coq-refman}.
Type-class solvers are unification based proof search procedures
reminiscent of Prolog, which back-chain lemmas taken
from a database of ``type-class instances''. Given this
analogy with Logic Programming we want to leverage the
Elpi meta programming language~\cite{tassi:hal-01637063},
a dialect of $\lambda$Prolog, already used to extend
Coq in various ways~\cite{tassi:hal-01637063,tassi:hal-01897468,gregoire:hal-03800154,newtc}.

>>>>

\section{Introduction}
\label{sec:intro}
We aim to implement a
form of proof search known as type-class resolution~\cite{wadler89,sozeau08}
for Coq's type system~\cite{Coq-refman}.
Type-class solvers are unification based proof search procedures
reminiscent of Prolog, which back-chain lemmas taken
from a database of ``type-class instances''. Given this
analogy with Logic Programming we want to leverage the
Elpi meta programming language~\cite{tassi:hal-01637063},
a dialect of $\lambda$Prolog, already used to extend
Coq in various ways~\cite{tassi:hal-01637063,tassi:hal-01897468,gregoire:hal-03800154,newtc}.
